---
title: "Final Project - Bootstrap Confidence Intervals"
author: "Karthik Garimella"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  html_notebook:
    toc: yes
    toc_float: yes
    highlight: pygments
    theme: paper
    toc_depth: 4
---

```{r, echo=FALSE}
library(ggplot2)
```


# Getting the data
```{r}
data <- read.csv('final_project data.csv', row.names = 1)
data
```


### Points
```{r, echo=FALSE}
data[, 'Points']
```

### Expected Points
```{r, echo=FALSE}
data[, 'Expected.Points']
```


# Point and Line Plots
```{r, echo=FALSE}
ggplot(data, aes(x = Season, group = 1)) +
  geom_point(aes(y = Points, color = 'Points'), size = 3) +
  geom_point(aes(y = Expected.Points, color = 'Expected.Points'), size = 3)+
  geom_line(aes(y = Points, color = 'Points'))+
  geom_line(aes(y = Expected.Points, color = 'Expected.Points'))+
  ggtitle('Points & Exp. Points throughout last 9 seasons')+
  theme_minimal()+
  theme(
    panel.grid.major = element_line(color = "darkgray", linetype = "dashed"),
    panel.grid.minor = element_line(color = "gray", linetype = "dotted")
  )
```

```{r, echo=FALSE}
ggplot(data, aes(x = Season, group = 1)) +
  geom_point(aes(y = Goals, color = 'Goals'), size = 3) +
  geom_point(aes(y = Expected.Goals, color = 'Expected.Goals'), size = 3)+
  geom_line(aes(y = Goals, color = 'Goals'))+
  geom_line(aes(y = Expected.Goals, color = 'Expected.Goals'))+
  ggtitle('Goals & Exp. Goals throughout last 9 seasons')+
  theme_minimal()+
  theme(
    panel.grid.major = element_line(color = "darkgray", linetype = "dashed"),
    panel.grid.minor = element_line(color = "gray", linetype = "dotted")
  )
```



```{r, echo=FALSE}
ggplot(data, aes(x = Season, group = 1)) +
  geom_point(aes(y = Goals, color = 'Goals'), size = 3) +
  geom_point(aes(y = Goals.Against, color = 'Goals.Against'), size = 3)+
  geom_line(aes(y = Goals, color = 'Goals'))+
  geom_line(aes(y = Goals.Against, color = 'Goals.Against'))+
  ggtitle('Goals v Goals Against throughout last 9 seasons')+
  theme_minimal()+
  theme(
    panel.grid.major = element_line(color = "darkgray", linetype = "dashed"),
    panel.grid.minor = element_line(color = "gray", linetype = "dotted")
  )

```
```{r, echo=FALSE}
ggplot(data, aes(x = Season, group = 1)) +
  geom_point(aes(y = Expected.Goals.Against, color = 'Expected.Goals.Against'), size = 3) +
  geom_point(aes(y = Goals.Against, color = 'Goals.Against'), size = 3)+
  geom_line(aes(y = Expected.Goals.Against, color = 'Expected.Goals.Against'))+
  geom_line(aes(y = Goals.Against, color = 'Goals.Against'))+
  ggtitle('Goals Against & Expected Goals Against throughout last 9 seasons')+
  theme_minimal()+
  theme(
    panel.grid.major = element_line(color = "darkgray", linetype = "dashed"),
    panel.grid.minor = element_line(color = "gray", linetype = "dotted")
  )

```


## Mean of Points
```{r, echo=FALSE}
mean(data$Points)
```

## Mean of Expected Points
```{r, echo=FALSE}
mean(data$Expected.Points)
```
<br>
Although the mean is close for Points and Expected Points, how much confident are we that there is an over-performance


Doing the bootstrap re-sampling to find difference between points, expected points and see the confidence intervals. Checks if they overlap or not, if they do not, then it shows considerable over-performance. If not, then the over-performance is not statistically significant.



# Declaring Simulation Samples
```{r}
B <- 1000
N <- 5000
```


```{r, echo=FALSE}
n <- nrow(data)

data_points <- data[ ,'Points']

data_exp_points <- data[ , 'Expected.Points']
```

# Bootstrap Sampling for Expected Points and Points
```{r, echo=FALSE}
data_points_boot <- replicate(B, data_points[sample.int(n, n, replace = TRUE)])

data_exp_points_boot <- replicate(B, data_exp_points[sample.int(n, n, replace = TRUE)])

# Using apply() to get mean() of the boot samples
data_points_mean <- apply(data_points_boot, 2, mean)

data_exp_points_mean <- apply(data_exp_points_boot, 2, mean)

```



```{r, echo=FALSE}
final_data_points_mean <- mean(data_points_mean)

final_data_exp_points_mean <- mean(data_exp_points_mean)
```

### Correlation between the data
```{r, echo=FALSE}
cor(data_exp_points_mean, data_points_mean)
```


### Histogram of Samples Generated
```{r, echo=FALSE}
hist(data_points_mean, breaks = 100, prob = TRUE, col = 'green',
  main = 'Histogram for Points & Exp. Points Simulation', density = 1, xlim = c(55, 80),
  xlab = 'Points & Exp. Points')

hist(data_exp_points_mean, breaks = 100, prob = TRUE, col = 'red',
  density = 0.9, add = TRUE, alpha = 0.5)

legend('topright', legend = c('Actual Points', 'Expected Points'),
       fill = c('green', 'red'))
```

### Boxplot of Points and Exp. Points
```{r, echo=FALSE}
box_data <- data.frame(
  Group = rep(c("Expected Points", "Actual Points"), each = length(data_exp_points_mean)),
  Value = c(data_exp_points_mean, data_points_mean)
)

# Create a box plot
ggplot(box_data, aes(x = Group, y = Value, fill = Group)) +
  geom_boxplot()+
  labs(title = "Box Plot of Expected Points vs. Actual Points",
       x = "Group",
       y = "Value")
```



### Standard Normal Confidence Interval
```{r}
norm_ci_func <- function(x){
  z <- qnorm(.975)
  
  norm_mean <- mean(x)
  norm_sd <- sd(x)
  norm_ci <- norm_mean + c(-1 , 1) * z * norm_sd
  
  return(norm_ci)
}

```

### Basic Bootstrap Confidence Interval
```{r}
basic_boot_ci_func <- function(x,y){
  basic_boot_ci <- 2 * mean(x) - quantile(y, c(0.975, 0.025))
}

```

### Percentile Bootstrap Confidence Interval
```{r}
percent_ci_func <- function(x){
  return(quantile(x, c(0.025, 0.975)))
}

```


### BCa Bootstrap Confidence Intervals

```{r}
bca_boot_ci_func <- function(x,y){

theta_hat <- mean(x)
p <- mean(y < theta_hat)
z0_hat <- qnorm(p)

point_jack <- sapply(1:n, function(i) mean(x[-i]))
a_hat <- sum((mean(point_jack) - point_jack) ^3) / (6 * sum((point_jack - mean(point_jack))^2) ^(3/2))

z <- qnorm(c(0.025, 0.975))

alpha <- pnorm(z0_hat + (z0_hat+z)/(1-a_hat*(z0_hat+z)))

bca_ci_points <- quantile(y, alpha)

return(bca_ci_points)

}
```



# Monte Carlo Simulation and Bootstrapping

```{r, echo=FALSE}
points_mu <- mean(data[, 'Points'])
exp_points_mu <- mean(data[, 'Expected.Points'])
```


```{r, eval=FALSE, echo=FALSE}
B <- 1000
N <- 5000
n <- nrow(data)
```


```{r, eval=FALSE, echo=FALSE}
Temp_Points_df <- data.frame()
Points_df <- data.frame()
Exp.Points_df <- data.frame()
```

### Standard Normal CI
```{r, eval=FALSE}
n_list <- list(5, 7, 9)

for(lst in n_list){
for(rep in 1:N){ # Monte Carlo Simulation

  # Bootstrap Sampling
  points_boot <- replicate(B, data_points[sample.int(lst, lst, replace = TRUE)]) 
  exp_points_boot <- replicate(B, data_exp_points[sample.int(lst, lst, replace = TRUE)])
  
  data_points_mean <- apply(points_boot, 2, mean)
  data_exp_points_mean <- apply(exp_points_boot, 2, mean)
  
  # Mean of Samples
  mean_points_boot <- mean(data_points_mean) # Mean of Bootstrap Sample Points
  mean_exp_points_boot <- mean(data_exp_points_mean)
  
  # Standard Normal CI
  norm_ci_points <- apply(points_boot, 1, norm_ci_func) # Points
  norm_ci_exp_points <- apply(exp_points_boot, 1, norm_ci_func) #norm_ci_func(data_exp_points_mean) # Exp Points
  
  # Cov Prob and Width for Points
  coverage_probability <- mean(points_mu >= norm_ci_points[1] & points_mu <= norm_ci_points[2])
  average_width <- norm_ci_points[2] - norm_ci_points[1]
  
  # Cov Prob and Width for Exp. Points
  exp_coverage_probability <- mean(exp_points_mu >= norm_ci_exp_points[1] & points_mu <= norm_ci_exp_points[2])
  exp_average_width <- norm_ci_exp_points[2] - norm_ci_exp_points[1]
  
}

cov_se <- sqrt(mean(coverage_probability) * (1 - mean(coverage_probability))/N)
cov_exp_se <- sqrt(mean(exp_coverage_probability) * (1 - mean(exp_coverage_probability))/N)

Temp_Points_df <- data.frame(Method = 'Standard Normal',
                             Column = 'Points', n = lst,
                             mean = mean_points_boot,
                          Coverage_Prob = mean(coverage_probability),
                          LCL = norm_ci_points[1],
                          UCL = norm_ci_points[2],
                          CovLCL = mean(coverage_probability) - 2 * cov_se,
                          CovUCL = mean(coverage_probability) + 2 * cov_se,
                          Width = mean(average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
  
Temp_Points_df <- data.frame(Method = 'Standard Normal',
                             Column = 'Exp. Points', n = lst,
                             mean = mean_exp_points_boot,
                          Coverage_Prob = mean(exp_coverage_probability),
                          LCL = norm_ci_exp_points[1],
                          UCL = norm_ci_exp_points[2],
                          CovLCL = mean(exp_coverage_probability) - 2 * cov_exp_se,
                          CovUCL = mean(exp_coverage_probability) + 2 * cov_exp_se,
                          Width = mean(exp_average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)

}
```



### Basic Bootstrap CI
```{r, eval=FALSE, echo=FALSE}
for (lst in n_list) {
for(rep in 1:N){ # Monte Carlo Simulation

  # Bootstrap Sampling
  points_boot <- replicate(B, data_points[sample.int(lst, lst, replace = TRUE)]) 
  exp_points_boot <- replicate(B, data_exp_points[sample.int(lst, lst, replace = TRUE)])
  
  data_points_mean <- apply(points_boot, 2, mean)
  data_exp_points_mean <- apply(exp_points_boot, 2, mean)
  
  # Mean of Samples
  mean_points_boot <- mean(data_points_mean) # Mean of Bootstrap Sample Points
  mean_exp_points_boot <- mean(data_exp_points_mean)
  
  # Basic Boot CI
  # basic_ci_points <- basic_boot_ci_func(data$Points, data_points_mean) # Points
  # basic_ci_exp_points <- basic_boot_ci_func(data$Exp.Points, data_exp_points_mean) # Exp Points
  
  basic_ci_points <- basic_boot_ci_func(data_points, points_boot)
    # apply(data_points, 1, basic_boot_ci_func, y = points_boot)
  basic_ci_exp_points <- basic_boot_ci_func(data_exp_points, exp_points_boot)
  
  
  # Cov Prob and Width for Points
  coverage_probability <- mean(points_mu >= basic_ci_points[1] & points_mu <= basic_ci_points[2])
  average_width <- basic_ci_points[2] - basic_ci_points[1]
  # Cov Prob and Width for Exp. Points
  exp_coverage_probability <- mean(exp_points_mu >= basic_ci_exp_points[1] & points_mu <= basic_ci_exp_points[2])
  exp_average_width <- basic_ci_exp_points[2] - basic_ci_exp_points[1]
  
}

cov_se <- sqrt(mean(coverage_probability) * (1 - mean(coverage_probability))/N)
cov_exp_se <- sqrt(mean(exp_coverage_probability) * (1 - mean(exp_coverage_probability))/N)

Temp_Points_df <- data.frame(Method = 'Basic Bootstrap',
                             Column = 'Points', n = lst,
                             mean = mean_points_boot,
                          Coverage_Prob = mean(coverage_probability),
                          LCL = basic_ci_points[1],
                          UCL = basic_ci_points[2],
                          CovLCL = mean(coverage_probability) - 2 * cov_se,
                          CovUCL = mean(coverage_probability) + 2 * cov_se,
                          Width = mean(average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
  
Temp_Points_df <- data.frame(Method = 'Basic Bootstrap',
                             Column = 'Exp. Points', n = lst,
                             mean = mean_exp_points_boot,
                          Coverage_Prob = mean(exp_coverage_probability),
                          LCL = basic_ci_exp_points[1],
                          UCL = basic_ci_exp_points[2],
                          CovLCL = mean(exp_coverage_probability) - 2 * cov_exp_se,
                          CovUCL = mean(exp_coverage_probability) + 2 * cov_exp_se,
                          Width = mean(exp_average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)

}
```



### Percentile Bootstrap
```{r, eval=FALSE, echo=FALSE}
for(lst in n_list){
for(rep in 1:N){ # Monte Carlo Simulation

  # Bootstrap Sampling
  points_boot <- replicate(B, data_points[sample.int(lst, lst, replace = TRUE)]) 
  exp_points_boot <- replicate(B, data_exp_points[sample.int(lst, lst, replace = TRUE)])
  
  data_points_mean <- apply(points_boot, 2, mean)
  data_exp_points_mean <- apply(exp_points_boot, 2, mean)
  
  # Mean of Samples
  mean_points_boot <- mean(data_points_mean) # Mean of Bootstrap Sample Points
  mean_exp_points_boot <- mean(data_exp_points_mean)
  
  # Basic Boot CI
  percent_ci_points <- apply(points_boot, 1, percent_ci_func)
  #percent_ci_func(data_points_mean) # Points
  percent_ci_exp_points <- apply(exp_points_boot, 1, percent_ci_func)    
  #percent_ci_func(data_exp_points_mean) # Exp Points
  
  # Cov Prob and Width for Points
  coverage_probability <- mean(points_mu >= percent_ci_points[1] & points_mu <= percent_ci_points[2])
  average_width <- percent_ci_points[2] - percent_ci_points[1]
  # Cov Prob and Width for Exp. Points
  exp_coverage_probability <- mean(exp_points_mu >= percent_ci_exp_points[1] & points_mu <= percent_ci_exp_points[2])
  exp_average_width <- percent_ci_exp_points[2] - percent_ci_exp_points[1]
  
}

cov_se <- sqrt(mean(coverage_probability) * (1 - mean(coverage_probability))/N)
cov_exp_se <- sqrt(mean(exp_coverage_probability) * (1 - mean(exp_coverage_probability))/N)

Temp_Points_df <- data.frame(Method = 'Percentile',
                             Column = 'Points', n = lst,
                             mean = mean_points_boot,
                          Coverage_Prob = mean(coverage_probability),
                          LCL = basic_ci_points[1],
                          UCL = basic_ci_points[2],
                          CovLCL = mean(coverage_probability) - 2 * cov_se,
                          CovUCL = mean(coverage_probability) + 2 * cov_se,
                          Width = mean(average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
  
Temp_Points_df <- data.frame(Method = 'Percentile',
                             Column = 'Exp. Points', n = lst,
                             mean = mean_exp_points_boot,
                          Coverage_Prob = mean(exp_coverage_probability),
                          LCL = basic_ci_exp_points[1],
                          UCL = basic_ci_exp_points[2],
                          CovLCL = mean(exp_coverage_probability) - 2 * cov_exp_se,
                          CovUCL = mean(exp_coverage_probability) + 2 * cov_exp_se,
                          Width = mean(exp_average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
}
```


### BCa Boostrap
```{r, eval=FALSE, echo=FALSE}
for(lst in n_list){
for(rep in 1:N){ # Monte Carlo Simulation

  # Bootstrap Sampling
  points_boot <- replicate(B, data_points[sample.int(lst, lst, replace = TRUE)]) 
  exp_points_boot <- replicate(B, data_exp_points[sample.int(lst, lst, replace = TRUE)])
  
  data_points_mean <- apply(points_boot, 2, mean)
  data_exp_points_mean <- apply(exp_points_boot, 2, mean)
  
  # Mean of Samples
  mean_points_boot <- mean(data_points_mean) # Mean of Bootstrap Sample Points
  mean_exp_points_boot <- mean(data_exp_points_mean)
  
  # Basic Boot CI
  bca_ci_points <- bca_boot_ci_func(data_points, points_boot)
  #apply(data$Points, 1, bca_boot_ci_func, y = points_boot) # Points
  bca_ci_exp_points <- bca_boot_ci_func(data_exp_points, exp_points_boot)
  #apply(data$Exp.Points, 1, bca_boot_ci_func, y = exp_points_boot) # Exp Points
  
  # Cov Prob and Width for Points
  coverage_probability <- mean(points_mu >= bca_ci_points[1] & points_mu <= bca_ci_points[2])
  average_width <- bca_ci_points[2] - bca_ci_points[1]
  # Cov Prob and Width for Exp. Points
  exp_coverage_probability <- mean(exp_points_mu >= bca_ci_exp_points[1] & points_mu <= bca_ci_exp_points[2])
  exp_average_width <- bca_ci_exp_points[2] - bca_ci_exp_points[1]
  
}

cov_se <- sqrt(mean(coverage_probability,  na.rm = TRUE) * (1 - mean(coverage_probability,  na.rm = TRUE))/N)
cov_exp_se <- sqrt(mean(exp_coverage_probability,  na.rm = TRUE) * (1 - mean(exp_coverage_probability,  na.rm = TRUE))/N)

Temp_Points_df <- data.frame(Method = 'BCa',
                             Column = 'Points', n = lst,
                             mean = mean_points_boot,
                          Coverage_Prob = mean(coverage_probability, na.rm = TRUE),
                          LCL = bca_ci_points[1],
                          UCL = bca_ci_points[2],
                          CovLCL = mean(coverage_probability, na.rm = TRUE) - 2 * cov_se,
                          CovUCL = mean(coverage_probability, na.rm = TRUE) + 2 * cov_se,
                          Width = mean(average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
  
Temp_Points_df <- data.frame(Method = 'BCa',
                             Column = 'Exp. Points', n = lst,
                             mean = mean_exp_points_boot,
                          Coverage_Prob = mean(exp_coverage_probability, na.rm = TRUE),
                          LCL = bca_ci_exp_points[1],
                          UCL = bca_ci_exp_points[2],
                          CovLCL = mean(exp_coverage_probability, na.rm = TRUE) - 2 * cov_exp_se,
                          CovUCL = mean(exp_coverage_probability, na.rm = TRUE) + 2 * cov_exp_se,
                          Width = mean(exp_average_width))
Points_df  <- bind_rows(Points_df , Temp_Points_df)
}
```


```{r, echo=FALSE, eval=FALSE}
save(Points_df, file = 'Points_df.Rdata')
```

```{r, echo=FALSE}
load('Points_df.Rdata')
```

### Created DataFrame
```{r, echo=FALSE}
Points_df
```


### Plotting
```{r, echo=FALSE}
ggplot(Points_df[Points_df$Method == 'Standard Normal', ], aes(x = Column, col = Column))+
  # geom_line(aes(y = Width ))+
  geom_point(aes(y = mean, pch = Method))+
  geom_errorbar(aes(y = Coverage_Prob, ymin = LCL, ymax = UCL), width = .5)+
  # geom_hline(aes(yintercept = ConfLevel), col = 'black', lty = 1, lwd = 0.5)+
  facet_wrap(~n, ncol = 3, scales = 'fixed')+
  labs(title = "Points v Exp. Points CI for altering 'n'")+
  ylab('Standard Normal CI')+
  xlab('Points or Exp. Points')
```
```{r, echo=FALSE}
ggplot(Points_df[Points_df$Method == 'Basic Bootstrap', ], aes(x = Column, col = Column))+
  # geom_line(aes(y = Width ))+
  geom_point(aes(y = mean, pch = Method))+
  geom_errorbar(aes(y = Coverage_Prob, ymin = LCL, ymax = UCL), width = .5)+
  # geom_hline(aes(yintercept = ConfLevel), col = 'black', lty = 1, lwd = 0.5)+
  facet_wrap(~n, ncol = 3, scales = 'fixed')+
  labs(title = "Points v Exp. Points CI for differing 'n'")+
  ylab('Basic Bootstrap CI')+
  xlab('Points or Exp. Points')
```

```{r, echo=FALSE}
ggplot(Points_df[Points_df$Method == 'Percentile', ], aes(x = Column, col = Column))+
  # geom_line(aes(y = Width ))+
  geom_point(aes(y = mean, pch = Method))+
  geom_errorbar(aes(y = Coverage_Prob, ymin = LCL, ymax = UCL), width = .5)+
  # geom_hline(aes(yintercept = ConfLevel), col = 'black', lty = 1, lwd = 0.5)+
  facet_wrap(~n, ncol = 3, scales = 'fixed')+
  labs(title = "Points v Exp. Points CI for differing 'n'")+
  ylab('Percentile CI')+
  xlab('Points or Exp. Points')
```



```{r, echo=FALSE}
ggplot(Points_df[Points_df$Method == 'BCa', ], aes(x = Column, col = Column))+
  # geom_line(aes(y = Width ))+
  geom_point(aes(y = mean, pch = Method))+
  geom_errorbar(aes(y = Coverage_Prob, ymin = LCL, ymax = UCL), width = .5)+
  # geom_hline(aes(yintercept = ConfLevel), col = 'black', lty = 1, lwd = 0.5)+
  facet_wrap(~n, ncol = 3, scales = 'fixed')+
  labs(title = "Points v Exp. Points CI for differing 'n'")+
  ylab('BCa CI')+
  xlab('Points or Exp. Points')
```







```{r, echo=FALSE}
# Error Bar Plot for Confidence Intervals
ggplot(Points_df, aes(x = Column, y = (LCL + UCL) / 2, ymin = LCL, ymax = UCL)) +
  geom_errorbar(width = .5, position = position_dodge(0.8), color = "steelblue") +
  geom_point(aes(col = Method), position = position_dodge(0.8), size = 3) +
  labs(title = "Confidence Interval Comparison", y = "Mean of CI", ymin = "Lower Bound", ymax = "Upper Bound") +
  theme_minimal()+
  facet_wrap(~n , scales = 'free_y', ncol = 2)+
  labs(title = "Confidence Interval Comparison for alternating 'n'")+
  ylab('Confidence Intervals')+
  xlab('Points or Exp. Points')

```


```{r, echo=FALSE}
ggplot(Points_df, aes(x = Column, col = Method))+
  geom_point(aes(y = mean, pch = Method))+
  geom_hline(yintercept = mean(data$Points), linetype = "dashed", color = "red")+
  geom_hline(yintercept = mean(data$Expected.Points), linetype = "dashed", color = "blue")+
  facet_wrap(~n, ncol= 2, scales = 'free')+
  labs(title = "Mean for differing 'n'")+
  ylab('Mean')+
  xlab('Points or Exp. Points')
```


```{r, echo=FALSE}
ggplot(Points_df, aes(x = Column, col = Method))+
  geom_point(aes(y = Width, pch = Method))+
  facet_wrap(~n, ncol= 2, scales = 'free')+
  labs(title = "Average Width for differing 'n'")+
  ylab('Avg. Width')+
  xlab('Points or Exp. Points')
```

```{r, echo=FALSE}
ggplot(Points_df, aes(x = n, col = Method))+
  geom_line(aes(y = Width),  lty = 2 )+
  geom_point(aes(y = Width, pch = Method))+
  facet_wrap(~Method, ncol= 2, scales = 'free')+
  labs(title = "Average Width for differing CI")+
  ylab('Avg. Width')+
  xlab('n')
```

Due to the extremely small sample size and real world data, the bootstrap sampling methods do not create extreme outliers.


```{r, echo=FALSE}
ggplot(Points_df, aes(x = n, col = Method)) +
  geom_point(aes(y = Coverage_Prob)) +
  facet_wrap(~ Method)+
  labs(title = "Coverage Probability for altering CI's")+
  ylab('Coverage Probability')+
  xlab('n')
```


# Conclusion

Although the sample size is small and it is improbable to come up with more real life data without waiting, we can use Bootstrapping and Monte Carlo simulations to generate data and estimate a population mean. We can statistically say that there was slight over-performance given the minute amount of data. We can confirm with the given data that the true parameter i.e. the mean of the Points and Expected Points does lie in the confidence interval with surety in every simulation.



























